---
title: "Exploratory Data Analysis"
author: "Sam Kramer"
date: "11/24/2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(leaps)
library(tidyverse)
```


# Read Data
```{r, echo=FALSE}
# LOAD DATA - MAY NOT WORK ON YOUR COMP

MATT <- FALSE

mattswd = '/Users/mathieurolfo/Dropbox/Coterm/Fall 2017-2018/STATS202/kaggle_project'
samswd <- "/Users/Kramer/Dropbox/School/Fall/STATS 202/kaggle_project/"

if (MATT) {
  trainfile = paste(mattswd, '/data/train.csv', sep='')
  testfile = paste(mattswd, '/data/test.csv', sep='')
} else {
  trainfile = paste(samswd, '/data/train.csv', sep='')
  testfile = paste(samswd, '/data/test.csv', sep='')
}

df = read.csv(trainfile, header=TRUE)
testData = read.csv(testfile, header=TRUE)
```

## Calculate Building Volumes
```{r}
df <- df %>% 
  mutate(Floor.Area = Surface.Area - Wall.Area - Roof.Area) %>% 
  mutate(Volume = Floor.Area * Height)

df %>% 
  distinct(Volume)
```

# EDA

```{r, fig.width = 10, fig.height = 10}
# pairs.plot <- GGally::ggpairs(df)

# ggsave("../figures/pairwise scatter.pdf", pairs.plot, width=12, height=12)
```

```{r}
df %>% 
  ggplot(aes(Surface.Area, Outcome)) +
  geom_point(aes(color = factor(Roof.Area))) + 
  facet_grid(Height ~ Glazing.Area, labeller = label_both) + 
  theme(legend.position = "bottom")
```

```{r}
df %>% 
  ggplot(aes(Surface.Area, Outcome)) +
  geom_point(aes(color = factor(Roof.Area))) + 
  facet_grid(~Glazing.Area, labeller = label_both) + 
  theme(legend.position = "bottom")
```

```{r}
df %>% 
  ggplot(aes(Surface.Area, Outcome)) +
  geom_point(aes(color = factor(Glazing.Area))) +
  facet_wrap(~Volume, labeller = label_both) + 
  theme(legend.position = "bottom")
```


# Observations

* Relative Compactness looks like a function of surface area, and they're REALLY collinear, so we should only use one of these.

* It looks like these simulations tried to test different building shapes for a few different fixed volumes. There are 12 different surface areas (same for relative compactness), 7 different wall areas, 4 different roof areas, and 2 different heights. I tried to estimate building volume by calculating floor area and multiplying by building height, and there are only 3 distinct volumes in the dataset. Maybe we could use this as a predictor?

* The smallest volume buildings can have 2 different roof areas, but each of the two larger volumes only has one height

* All buildings with the shorter height have >680 surface area. **These buildings use significantly less energy than the smaller surface area buildings that are taller.**

* I think Glazing Distribution should be a categorical variable


## Important Factors

* Surface Area

* Height

* Glazing Area

* 